Building the Million Transcriptome Ocular Meta-Atlas

### 2021-01-17 manuscript_00.Rmd
sup fig

```{r projection_fig, fig.width=12, fig.height=10,  fig.cap=projection_fig_cap, echo=FALSE, message = FALSE}
projection_fig_cap <- supFig_cap(name='projection_fig', caption =  'bloop')
1 + 1
```

>>>>

```{r projection_fig, fig.width=12, fig.height=10,  fig.cap=projection_fig_cap, echo=FALSE, message = FALSE}
input[['pt_size_back']] <- 0
input[['pt_size_meta']] <- 4
#input[['gene_and_meta_scatter_tech']] <- 'Droplet'
input[['meta_column_transform']] <- 'None'
input[['meta_filter_cat']] <- 'CellType_predict'
input[['meta_filter_on']] <- c('RPE')
rpe <- make_meta_scatter_umap_plot(input, mf, meta_filter,
                                   celltype_predict_labels,
                                   celltype_labels,
                                   tabulamuris_predict_labels,
                                   cluster_labels,
                                   cat_to_color_df
)
#

colab_p <- ggdraw() + draw_image("figs_and_tables/colab_screenshot.png", scale = 0.7)

plot_grid(rpe$plot , colab_p)
